\thetitle

### 2018-02-04 TeX/manuscript.tex
Symbol figure

\documentclass{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath}
\usepackage{setspace, fancyhdr, hyperref, xcolor, tikz, subcaption, float, marginnote, changebar}
\usepackage[normalem]{ulem}

@@

		In figure 13 (section 2.9), a simple network either adds or multiplies two input values depending on which is greater. We can say that the group of the two output neurons (one being an adder and one a multiplier) is a symbol, which represents the function that was performed.

>>>>

\documentclass{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath}
\usepackage{setspace, fancyhdr, hyperref, xcolor, tikz, subcaption, float, marginnote, changebar}
\usepackage[normalem]{ulem}
\usetikzlibrary{fit}

@@

		In figure 13 (section 2.9), a simple network either adds or multiplies two input values depending on which is greater. We can say that the group of the two output neurons (one being an adder and one a multiplier) is a symbol, which represents the function that was performed. The categorization function would simply check which activity is higher in each of the two neurons and will say that the symbol represents the function of whichever has the higher activity.

			\node[output] (o1) at (0,6) {0 or 1};
			\node[output] (o2) at (4,6) {0 or 1};

			\node[draw,rounded corners,color=red,line width=0.5mm,inner sep=2mm,label=above:Symbol S,fit=(o1) (o2) (o1) (o2)] {};

		The corresponding definition of Symbol S is the following:

		\[ S =
		\begin{cases} 
			'Addition' & [1,0] \\
			'Multiplication' & [0,1]
		\end{cases}
		\]

		\caption{A 'router' network expressed using a Symbol}
